---
title: "new_synergies"
author: "Laura Menicacci"
date: "2023-09-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# libraries
library('purrr')
library(dplyr)
library(readxl)
library(tidyverse)
#library(combinat)  # For generating combinations
library(kableExtra)
library(gridExtra)

# data
data <- readRDS(".\\policy_out_filtered.RDS")
oecd <- read.csv(".\\OECD_data_preprocessed_august_23.csv", sep = ",")

```

# Data preparation 

```{r}

# List of data frames to be joined out of the RDS file
break_dfs <- list(data[[3]][[1]], data[[3]][[2]], data[[3]][[3]], 
                  data[[3]][[4]], data[[3]][[5]], data[[3]][[6]], 
                  data[[3]][[7]], data[[3]][[8]])

# Use Reduce and full_join to join all data frames in the list
breaks <- Reduce(function(x, y) full_join(x, y), break_dfs)


# Do the same for the policies attributed
policies_2y_dfs <- list(data[[6]][[1]], data[[6]][[2]], data[[6]][[3]], 
                        data[[6]][[4]], data[[6]][[5]], data[[6]][[6]], 
                        data[[6]][[7]], data[[6]][[8]])

policies_2y <- Reduce(function(x, y) full_join(x, y), policies_2y_dfs)

# IRL_2018_2022 has one policy/break in buildings in 2019, and 3 in transport between 2019-2021
# IRL_2013_2017 has one policy/break in buildings in 2015, and 2 in transport between 2014-2017
# DNK_2018_2022 has one policy/break in buildings in 2019, and 2 in transport in 2018, 2022

policies_2y <- policies_2y %>% 
  mutate(unique_break_identifier = case_when(Module == "Industry" ~ paste0("I_", unique_break_identifier),
                                             Module == "Buildings" ~ paste0("B_", unique_break_identifier),
                                             Module == "Electricity" ~ paste0("E_", unique_break_identifier), 
                                             Module == "Transport" ~ paste0("T_", unique_break_identifier))) 

policies_2y[67, 3] <- "Congestion Charges" # adjust congestion charge which is spelled differently
oecd[152, 3] <- "Congestion Charges" # adjust congestion charge which is spelled differently

# add missing USA 2007 MEPS to OECD
MEPS_USA_2007 <- policies_2y[95,] 

oecd <- bind_rows(oecd, MEPS_USA_2007)
oecd <- oecd[,1:20]

# check number of breaks is right, should be 56
length(unique(policies_2y$unique_break_identifier))

```

# Single policies

## Calculate the average effect size for single policies

Found ATE for 13 single policy types out of 44

```{r}

single_policy_breaks <- policies_2y %>%
  group_by(unique_break_identifier) %>% # Group by unique_break_identifier 
  summarize(count = n()) %>% # Count number of policy matches
  filter(count == 1) %>%  # Filter to include only policies with single policy matches
  pull(unique_break_identifier)

average_effect_sizes <- policies_2y %>%
  filter(unique_break_identifier %in% single_policy_breaks) %>% # Filter for breaks with one #match
  select(Module, Policy, coeff, High_income) %>% 
  group_by(Policy) %>% # Group by policy
  mutate(average_effect_size = mean(coeff, na.rm = TRUE)) # Calculate the average effect size #for each single policy type

#write.csv(average_effect_sizes, ".\\average_effect_sizes.csv")

#known_effects <- policies_2y %>%
#  group_by(unique_break_identifier) %>% 
#  summarize(policy_mixes = paste(Policy, collapse = ","), # Policy mixes
#            effect_size_mix = unique(coeff, na.rm = TRUE)) %>% # Effect sizes of mixes
#  left_join(average_effect_sizes, by = c("policy_mixes" = "Policy")) # here we have the avg #effect sizes of single policies together with the known mixes effect
#
#write.csv(known_effects, ".\\known_effects.csv")

```

# Retrieve more single effects

Subtract known avg single effects from existing policy mixes to retrieve more average single effects. 

```{r}

#avg_effects_new <- read_csv(".\\average_effect_sizes_updated.csv") # do this manually: retrieved up to a total of 33 single policy types

```

## Ratio of detection/occurrence for single policies

```{r}
# Count policy introductions and tightenings by type 
occurrence <- oecd %>% 
  group_by(Policy) %>% 
  summarise(total_occurred = n())

# Count how often each policy type is detected (=matched with a break)
detection <- policies_2y %>% 
  group_by(Policy) %>%
  summarise(total_detected = n())

percent_detection <- left_join(detection, occurrence, by = "Policy") %>% 
  mutate(ratio = total_detected / total_occurred) # TOTAL DETECTION / TOTAL OCCURRENCE 
```

## Expected effect sizes for single policies

 * ratio = detection of the mix/total occurrence of the mix
 * avg effect size of mix 
 * expected = ratio * (avg) effect size
 
```{r}
expected_effect_size <- left_join(average_effect_sizes, percent_detection, by = "Policy") %>%
  mutate(expected_effect_size = ratio * average_effect_size)

# sanity check
table(is.na(expected_effect_size))

#write.csv(expected_effect_size, ".\\expected_effect_size_25_09.csv")

```

## Select all **existing** combinations among the 13 single policy effects (select only breaks that have policy mixes of which we have single effects) from the current policy mixes: these are the ones we can calculate

```{r}

breaks_with_mixes <- policies_2y %>%
  group_by(unique_break_identifier) %>%
  filter(n() > 1) %>% # Select breaks matching >1 policies
  summarize(policy_mixes = paste(Policy, collapse = ","), # Policy mixes
            detected_effect_size_mix = unique(coeff, na.rm = TRUE)) # Effect sizes of mixes


split_policies <- strsplit(breaks_with_mixes$policy_mixes, ',') # Split policy mixes into individual policies

valid_rows <- sapply(split_policies, function(policy_list) all(policy_list %in% expected_effect_size$Policy)) # Check if all policies in each row are present in expected_effect_size$Policy

# check: 
which(valid_rows == FALSE)

filt_breaks_with_mixes <- breaks_with_mixes[valid_rows, ] # Filter rows in breaks_with_mixes where all policies are valid

```

## 6) Compute expected effect size

```{r}

# for each combination 
  # sum the total expected effect size for the policy mix 

breaks_copy <- filt_breaks_with_mixes # create copy to avoid overwriting
breaks_copy$total_expected_effect <- 0  # Initialize the column

for (i in seq_along(breaks_copy$policy_mixes)) {  # for each policy mix 
  l <- unlist(strsplit(breaks_copy$policy_mixes[i], ","))  # split policy mix
  for (j in l) { # iterate over list of splitted mixes
    for (k in seq_along(expected_effect_size$Policy)) { # for each policy in expected_effect_size
      if (j == expected_effect_size$Policy[k]) { # check if policy is in our single effects df 
        breaks_copy[i, 4] <- breaks_copy$total_expected_effect[i] + as.numeric(expected_effect_size[k, 6]) # sum expected effects of single policies
      }
    }
  }
}

```


## 7) Compute synergy

```{r}
# for each row 
  # total detected effect - total expected effect 

breaks_copy$sinergy_effect <- 0

for (i in seq_along(breaks_copy$policy_mixes)) {
        # total detected - expected 
        breaks_copy[i, 5] <- breaks_copy[i, 3] - breaks_copy[i, 4]
      }

```

## 8) Results
```{r}

pdf(".\\synergies_v4_25_09.pdf", height=10, width=20)
grid.table(breaks_copy)
dev.off()

```

####################################################### 
# Another approach: try a different policy aggregation 

```{r}
# Define a mapping of old policy names to new policy names
# with conditions
policy_mapping <- data.frame(
  old_name = c("AirEmissionStandards", "Auction", "BanPhaseOutCoal",
               "Bans and Phaseouts passenger cars ICE", "Bans and Phaseouts Fossil Fuels Heating",
               "BuildingEnergyCodes", "Carbon tax", "CarbonTax Buildings",
               "Congestion Charges", "Emissions trading scheme",
               "EnergyEfficiencyMandates", "ETS Buildings", "ETS Electricity", "ETS Industry",
               "Excise Taxes Transport", "Excise Taxes Buildings", "Excise Taxes Electricity",
               "Investment in Rail Infrastructure", "Fossil Fuel Subsides Buildings", "Fossil Fuel Subsides Industry", "Fossil Fuel Subsides Transport", # Expenditure_RailVersusRoad = Investment in Rail Infrastructure?
               "Financial support", "Financing mechanism",
               "Financing Mechanism Buildings", "Financing Mechanism Industry", "FiT", # "FiT"?
               "Labels_Appliances", "Labels_PassengerCars", "MEPS",
               "MEPS_Appliances", "MEPS_ElectricMotors", "MEPS_T",
               "PlanningRenewablesExpansion", "RECs", "Renewable subsidy",
               "Subsidy", "Taxation"),
  new_name = c("airpollutionstandard", "subsidy_e", "ban_e", "ban_t",
               "ban_b", "buildingcode", "taxation_i", "taxation_b",
               "taxation_t", "taxation_e", "energyefficiency_i",
               "taxation_b", "taxation_e", "taxation_i", "taxation_t",
               "taxation_b", "taxation_e", "investment_t",
               "fuelsubsidyreform_b", "fuelsubsidyreform_i",
               "fuelsubsidyreform_t", "subsidy_b", "subsidy_i",
               "subsidy_b", "subsidy_i", "subsidy_e", "label_b",
               "label_t", "MEPS_t", "MEPS_b", "MEPS_i", "MEPS_t",
               "planning_e", "renewable_standard", "subsidy_e",
               "subsidy_b", "taxation_t")
)

# Function to map old policy names to new policy names with conditions
map_policy_names <- function(old_name, module) {
  new_name <- policy_mapping$new_name[policy_mapping$old_name == old_name]
  if (length(new_name) == 0) {
    return(old_name)  # If no mapping found, return the original name
  } else {
    if (module == "Industry" && new_name == "taxation_i") {
      return("taxation_i")
    } else if (module == "Buildings" && new_name == "subsidy_b") {
      return("subsidy_b")
    } else {
      return(new_name)
    }
  }
}

library('purrr')
# Apply the mapping function to the policies_2y DataFrame
policies_2y_new_mapping <- policies_2y %>%
  mutate(Policy = map2_chr(Policy, Module, map_policy_names))

# Apply also to the OECD data

oecd_new_mapping <- oecd %>% 
    mutate(Policy = map2_chr(Policy, Module, map_policy_names))

```

## Avg effect sizes

```{r}
single_policy_breaks_nm <- policies_2y_new_mapping %>%
  group_by(unique_break_identifier) %>% # Group by unique_break_identifier 
  summarize(count = n()) %>% # Count number of policy matches
  filter(count == 1) %>%  # Filter to include only policies with single policy matches
  pull(unique_break_identifier)

average_effect_sizes_nm <- policies_2y_new_mapping %>%
  filter(unique_break_identifier %in% single_policy_breaks) %>% # Filter for breaks with one #match
  group_by(Policy) %>% # Group by policy
  summarize(average_effect_size = mean(coeff, na.rm = TRUE)) # Calculate the average effect size #for each single policy type
```


# Another approach: add potential other priors????

From Patrick's suggestion --> "based on the policy mixes computable solely from the observed single y_i (i= 1,...13)", to also compute an *expected synergy effect* s" across those mixes, and substract it in the calculation above. 

first question: are there any policy mixes computable solely from the observed single y_i ? YES, 2. 

POTENTIAL ADDITIONAL INDICATORS TO THE RATIO COLUMN:
 - prior by sector
 - prior by income group
 - prior by introduction/tightening ???

```{r}
#### sector 
detection_by_sector <- policies_2y %>% group_by(Module) %>% summarise(detection_sector = n())
occurrence_by_sector <- oecd %>% group_by(Module) %>% summarise(occurrence_sector = n())

percent_detection_sector <- left_join(detection_by_sector, occurrence_by_sector, by = "Module") %>% 
  mutate(ratio_sector = detection_sector / occurrence_sector)

##### income
detection_by_income_group <- policies_2y %>% group_by(High_income) %>% summarise(detection_income = n())
occurrence_by_income_group <- oecd %>% group_by(High_income) %>% summarise(occurrence_income = n())

percent_detection_income <- left_join(detection_by_income_group, occurrence_by_income_group, by = "High_income") %>% 
  mutate(ratio_income_group = detection_income / occurrence_income)


```

add ratio of sector to expected_effect_size 
```{r}

expected_effect_size_sector <- left_join(average_effect_sizes, percent_detection_sector, by = "Module") 

expected_effect_size_sector_ratio <- left_join(expected_effect_size_sector, percent_detection, by = "Policy") 

expected_effect_size_sector_ratio_income <- left_join(expected_effect_size_sector_ratio, percent_detection_income, by = "High_income") %>% 
  mutate(expected_effect_size = ratio * average_effect_size, 
         expected_effect_size_sector = ratio_sector * ratio * average_effect_size,          expected_effect_size_sector_income = ratio_income_group *ratio_sector * ratio * average_effect_size)

```

## Expected effect sizes for single policies

 * ratio = detection of the mix/total occurrence of the mix
 * avg effect size of mix 
 * expected = ratio * (avg) effect size
 
```{r}
expected_effect_size <- left_join(average_effect_sizes, percent_detection, by = "Policy") %>%
  mutate(expected_effect_size = ratio * average_effect_size)

# sanity check
table(is.na(expected_effect_size))

#write.csv(expected_effect_size, ".\\expected_effect_size_25_09.csv")

```

what is the avg effect of 1 mix vs avg effect of single policy? 

```{r}
avg_effect_mix <- breaks_with_mixes %>% summarise(avg_effect_mix = mean(detected_effect_size_mix), 
                                                  median_effect_mix = median(detected_effect_size_mix)) # -0.2189362

avg_effect_single_pol <- average_effect_sizes %>% summarise(avg_effect_single_pol = mean(average_effect_size), 
                                                            median_effect_single = median(average_effect_size))
# -0.2199292

```

plot distribution

```{r}
breaks_with_mixes %>% 
  ggplot(aes(x=detected_effect_size_mix)) + geom_density()

average_effect_sizes %>% 
  ggplot(aes(x=average_effect_size)) + geom_density()
```

